\section{Test software}
\label{sec:software}


\subsection{Data sets}
\label{ssec:software:datasets}

The original acquisition software grants the operator some options that affect
the name of the waveform files. An acquisition-driving code was developed that
reduces those options and enforces a file name pattern:
\begin{verbatim}
waveform_CH<channel>_CHIMNEY_<chimney>_CONN_<cable>_POS_<position>_<index>.csv
\end{verbatim}
where the elements, defined in \cref{ssec:labelling}, are:
\begin{description}
  \item[\texttt{<channel>}] is the \emph{oscilloscope channel} the waveform is read from, which ranges from \texttt{1} to \texttt{4}
  \item[\texttt{<chimney>}] is in the form \texttt{<module><side><row>}, \texttt{WE07}
  \item[\texttt{<cable>}] is the label of the cable plugged in the test box, e.g.\ \texttt{V05}
  \item[\texttt{<position>}] is the setting of the test box switch
  \item[\texttt{<index>}] is a waveform counter;
    following Sergi's convention, this is a sequential number unique
    within waveforms on the same connector and oscilloscope channel.
    Assuming that 10 waveforms are taken per channel, position
    \texttt{POS\_1} will have indices from \texttt{1} to \texttt{10},
    \texttt{POS\_2} from \texttt{11} to \texttt{20}, and so on, up to
    \texttt{POS\_8} with indices \texttt{71} to \texttt{80}.
\end{description}

320 waveform files are expected per cable (10 waveforms for each of
32 channels, split in 4 oscilloscope channels and 8 test box switch
positions), and 5760 per chimney. These files are stored in separate
directories, one per chimney. The name of the directory follows the same
convention as above, that is \texttt{CHIMNEY\_<chimney>} (e.g.\ 
\texttt{CHIMNEY\_WE07}).
\\
The whole data set taken in the test session of August 2018 is currently
stored in Fermilab dCache at the path:
\begin{verbatim}
/pnfs/icarus/persistent/commissioning/connectivity/201808
\end{verbatim}



\subsection{Data format}
\label{ssec:software:dataformats}

Each waveform is stored in its own comma-separated value file (CSV). The file name follows the pattern described above. Each line in the file corresponding to a sample, totaling 10000 lines for each waveform. Each sample is described by values in floating point text representation, with scientific notation: time in seconds, and signal level in volt. For example:

\begin{verbatim}
0.0,2.08
1e-07,2.08
2e-07,2.12
[...]
\end{verbatim}

No metadata is saved in the file. This data format can be easily read directly by ROOT \texttt{TGraph}.



\subsection{Channel identification and mapping}
\label{ssec:software:channelMapping}

The data has been collected chimney by chimney and cable by cable, with 8 sequential acquisition runs per cable corresponding to the eight test box switch positions.
The following elements may be used for identifying a channel (see also \cref{ssec:labelling}):
\begin{description}
  \item[chimney] always represented as \texttt{<module><side><row>}, e.g.\ \texttt{WE07} (see \cref{fig:ChimneyLabelling})
  \item[flange] usually matches the chimney; in case of the end chimney, the flange is further identified by its position on it, as bottom (\texttt{b}), middle (\texttt{m}) or top (\texttt{t})
  \item[cable] a letter and a zero-padded two-digit cable number; cable number range is from 01 to 18 for short chimneys, 01 to 33 for the two top flanges of the end chimneys
  \item[channel] the number of channel within a cable, from 1 to 32
  \item[slot] the slot where the readout board (real or test) is inserted, from 1 to 9
  \item[side] the side of the cable the channel is on, left or right, always defined considering slot 1 to be on top (in the flanges of some end chimneys, this ends up swapping flange left and right labels with respect to the observer's)
  \item[switch position] one of eight possible positions for the test box switch, from 1 to 8
  \item[oscilloscope channel] number of the oscilloscope channel used for the digitization of the channel, from \texttt{CH1} to \texttt{CH4}
  \item[readout channel] the channel number on a flange according to the TPC readout firmware, from 0 to 575
  \item[board] the number of board in the readout minicrate, from 0 to 8
  \item[board channel] the number of channel within the readout board\cite{FEreadoutBoard}, from 0 to 63
\end{description}

The commonly used combinations of these elements to identify a channel are:
\begin{itemize}
  \item \emph{chimney/cable/channel}, currently the most standard notation
  \item \emph{flange/readout channel}, used in early readout pulse runs
  \item \emph{chimney/cable/switch position/oscilloscope channel}, used in connectivity test data storage
\end{itemize}

\Cref{table:NotationConversion} summarizes the relations between some of these elements.

\begin{table}
  {
    \small
    \begin{tabular}{|l|c|c|l|}
      \hline
      element    (symbol)   & range                                       & example        & conversions \\
      \hline
      chimney       ($C$)   & \texttt{[EW]}\texttt{[EW]}\texttt{<01-20>}  & \texttt{WE07}  & \\
      cable number  ($c$)   & 01--18, 01--33                              & 15             & \\
      channel       ($ch$)  & 1--32                                       & 27             & \\
      \hline
      slot          ($S$)   & 1--9                                        & 6              & $S = B + 1$ \\
      side          ($s$)   & 0 \emph{(L)}, 1 \emph{(R)}                  & 1 (R)          & $\theta\left(c \geq 10\right)$ \\ 
      switch pos.   ($p$)   & 1--8                                        & 7              & $(c - 1) \mod 4 + 1$ \\
      osc. channel  ($CH$)  & 1--4                                        & \texttt{CH3}   & $(c - 1) \div 4 + 1$ \\
      \hline
      flange        ($F$)   & \texttt{<$C$>}\texttt{[bmt]}                & \texttt{EE01m} & $F = C$ (removing any suffix if present) \\
      board         ($B$)   & 0--8                                        & 5              & $B = (c - 1) \mod 9$ \\
      board channel ($b$)   & 0--63                                       & 37             & $b = 32 s + (32 - ch)$ \\
      readout channel ($r$) & 0--575                                      & 357            & $r = 64 B + b$ \\
      \hline
    \end{tabular}
  }
  \label{table:NotationConversion}
  \caption{
    Conversion between elements used to identify a channel.
    All examples except for the flange refer to the same channel.
    Conversions are valid only for short chimneys.
  }
\end{table}


\subsection{Streamlined interactive data acquisition}
\label{ssec:software:streamlinedDAQ}

The original code by Sergi Castells required the operator to change
parameters on the command line on each acquisition, plus an additional step at the end of the test each connector, that is to reset a counter stored in a text file.

After a few interactions with this approach, we wrote additional
software (\emph{test driver}) automating most of the steps required from the operator. This enforced a specific procedure both for testing and for software setup.

The procedure comprises testing one chimney at a time, and proceeding from connection 18 (\texttt{V18} or \texttt{S18}) down to 1 (\texttt{V01} or \texttt{S01}), and on each connector test the channel switching the test box to the position from 1 to 8 in strict sequence. The whole sequence must be strictly followed.

More details about the software used for data acquisition and its setup can be found in \ref{appendix-A}.

